Lattice model

### 2017-04-01 oopsla17/lattice-model.tex
fix

\begin{defn}{(\emph{Points})}
  A \emph{point} is a Cartesian product (vector) of $\zinf$ values representing an
  $N$-dimensional point. The set of $N$-dimensional offsets is
  written $\zinf^N$. We denote sets of $N$-dimensionl points
by the set $\mathcal{P}(\zinf^N)$.

A set of $N$-dimensional points \emph{projected} into the set
of 1-dimensional points in the $i^{\text{th}}$ dimension by $\pi_i : \mathcal{P}(\zinf{})^{\mkern-19mu{N}} \to
  \mathcal{P}(\zinf{})$ where $i \in \mathsf{Fin}(N)$. We refer to this projected set as the \emph{$i^{th}$ components}.
\end{defn}

>>>>

\begin{defn}{(\emph{Points})}
  A $N$-dimenaional \emph{point} is a finite Cartesian product
  (vector) of $N$ values drawn from $\zinf$.

  The set of $N$-dimensional points is written $\zinf^N$ and the set
  of sets of $N$-dimensionl points is written $\mathcal{P}(\zinf^N)$.

A set of $N$-dimensional points can be \emph{projected} to the set of
1-dimensional points in the $i^{\text{th}}$ dimension by
$\pi_i : \mathcal{P}(\zinf{})^{\mkern-19mu{N}} \to
\mathcal{P}(\zinf{})$
where $i \in \mathsf{Fin}(N)$. We refer to this projected set as the
\emph{$i^{th}$ components}.
\end{defn}
